### 2011-06-14 article.tex
Now tracking article and added some tools

\documentclass[a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage[usenames,dvipsnames]{pstricks}
\usepackage{epsfig}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[nottoc, notlof, notlot]{tocbibind}

\begin{document}

\title{Sequences complexity}
\author{Axel Schumacher\\Télécom ParisTech\\Free Project}
\date{\today}

\maketitle

\newpage

\tableofcontents

\newpage

\section{Introduction}

As a student at Télécom ParisTech, I chose to follow the 'Non-classic languages paradigms' course with Samuel Tardieu, while working on a free project with Jean-Louis Dessalles.
Mr. Dessalles suggested a project based on a Komolgorov's complexity problem: given a small sequence of digits, shapes or characters, I had to design a small program able to complete this list as well as an eight-years old children.
The main purpose of this project is to apply Kolmogorov theory on the given list in order to compress it in a optimal and human way, so that we will then be able to extend that list using found compression process.
On the 'Non-classic languages paradigms' course, we learned small spread languages as Haskel, Scala or Factor, and we were also supposed to perform a small implementation project using one of those languages.
Factor is a quite memory-close language, able to perform back-tracking as well as Prolog using continuations.
Its powerful and non-standard architecture make him a very interesting language to work on.

\section{Problematic}

Humans' capability to compress and understand structures always fascinated computer sciences researchers.
Humans are able to perfectly perform tasks as recognizing a person's face, understand a language or, in our scope of interest, understand and complete a list of digits, alphabetics or shapes. Those tasks are very difficult to efficiently complete for machines, even using the most powerful computers.
That is why a huge domain of research still exists in this field, always in the same goal: give machines more and more of our 'human intelligence'.

\section{Basis}

Were now to try to light up some darks areas of this problem.
Let us imagine a very simple sequence:
$$1 2 2 3 3 3$$
Any eight-years old children would easily suggest that a good continuation of this sequence would be:
$$1 2 2 3 3 3 4 4 4 4$$
But how can one be so sure about it?
This is where we can introduce the notion of 'complexity', and more especially Kolmogorov's one:

\begin{thebibliography}{1}

\bibitem{A starting point} http://icc.enst.fr/PLC/Learn.html, section Complexity

\end{thebibliography}

\end{document}

### 2011-06-29 article.tex
Added references on article

@@
 \usepackage[nottoc, notlof, notlot]{tocbibind}
+\usepackage{hyperref}
 
@@
 
-As a student at Télécom ParisTech, I chose to follow the 'Non-classic languages paradigms' course with Samuel Tardieu, while working on a free project with Jean-Louis Dessalles.
+As a student at Télécom ParisTech, I chose to follow the 'Non-classic languages paradigms' course with Samuel Tardieu\cite{samuel}, while working on a free project with Jean-Louis Dessalles\cite{jld}.
 Mr.
 Dessalles suggested a project based on a Komolgorov's complexity problem: given a small sequence of digits, shapes or characters, I had to design a small program able to complete this list as well as an eight-years old children.
+\cite{starting_point}
+
 The main purpose of this project is to apply Kolmogorov theory on the given list in order to compress it in a optimal and human way, so that we will then be able to extend that list using found compression process.
 On the 'Non-classic languages paradigms' course, we learned small spread languages as Haskel, Scala or Factor, and we were also supposed to perform a small implementation project using one of those languages.
-Factor is a quite memory-close language, able to perform back-tracking as well as Prolog using continuations.
-Its powerful and non-standard architecture make him a very interesting language to work on.
+
+Factor\cite{factor} is a quite memory-close language, able to perform back-tracking as well as Prolog using continuations and working on a stack, like a logical sequence.
+Its powerful and non-standard architecture make him a very interesting language to work on, and that is why I chose to use it to implement my project.
 
@@
 Those tasks are very difficult to efficiently complete for machines, even using the most powerful computers.
-That is why a huge domain of research still exists in this field, always in the same goal: give machines more and more of our 'human intelligence'.
+That is why a huge domain of research still exists in that field, always in the same goal: give machines more and more of our 'human intelligence'.
 
@@
 
-Were now to try to light up some darks areas of this problem.
+We are now to try to light up some darks areas of this problem.
 Let us imagine a very simple sequence:
@@
 
-\begin{thebibliography}{1}
+"In algorithmic information theory (a subfield of computer science), the Kolmogorov complexity of an object, such as a piece of text, is a measure of the computational resources needed to specify the object." \cite{wikipedia_kolmogorov}
 
-\bibitem{A starting point} http://icc.enst.fr/PLC/Learn.html, section Complexity
+In other words, this complexity has the particularity to highly depends of using person, and is therefore really difficult to use inside a program.
+
+An other way to compute a list's complexity would be to use \textit{short term memory}, a list or tree containing last used elements.
+An access to one of those elements would be its address for example binary coded.
+This model is easily explainable considering that a human, if he was able to solve a problem using a specific operator, will naturally try it first when confronted to a new problem.
+This list is implemented but not used because of its unpredictable character.
+
+That is why in present version a standard binary coding is used to compute a list's complexity.
+
+Given a way to compute complexity, one can try to compress a list using \textit{operators} while resulting complexity is lower than initial sequence's one.
+
+\newpage
+
+\begin{thebibliography}{9}
+
+\bibitem{samuel} Samuel Tardieu's website: \url{http://www.rfc1149.net/}
+\bibitem{jld} Jean Louis Dessalles' website: \url{http://perso.telecom-paristech.fr/~jld/}
+\bibitem{starting_point} A starting point: \url{http://icc.enst.fr/PLC/Learn.html}, section Complexity
+\bibitem{factor} Factor language: \url{http://factorcode.org/}
+\bibitem{wikipedia_kolmogorov} Kolmogorov's Complexity on Wikiedia: \url{http://en.wikipedia.org/wiki/Kolmogorov_complexity}
 

### 2011-07-02 article.tex
Added three operator solution in article

@@
 Let us imagine a very simple sequence:
-$$1 2 2 3 3 3$$
+$$1\ 2\ 2\ 3\ 3\ 3$$
 Any eight-years old children would easily suggest that a good continuation of this sequence would be:
-$$1 2 2 3 3 3 4 4 4 4$$
+$$1\ 2\ 2\ 3\ 3\ 3\ 4\ 4\ 4\ 4$$
 But how can one be so sure about it?
@@
 
+Using this complexity, one could define $1\ 2\ 2\ 3\ 3\ 3$ as 'count from one and repeat each number as much as itself', which is really easier to understand, memorize and extend for an human than a random sequence, like a telephone or a credit card number.
+We will explore different ways to represent and manipulate such informations.
+
 An other way to compute a list's complexity would be to use \textit{short term memory}, a list or tree containing last used elements.
@@
 
-That is why in present version a standard binary coding is used to compute a list's complexity.
+That is why in present version a standard \textit{binary coding} is used to compute a list's complexity, with 0 costing 0.
 
 Given a way to compute complexity, one can try to compress a list using \textit{operators} while resulting complexity is lower than initial sequence's one.
+
+\section{Tentatives}
+
+\subsection{Three operators}
+
+At first, I thought about using Factor's \textit{tuples}, special sequences of fields easily sharable between descendants, like standard \textit{Object Oriented Programming}.
+
+I defined a tuple \textit{operator} containing a field named \textit{times}.
+Operator had the following methods, or \textit{generic functions} in Factor:
+\begin{itemize}
+  \item{cost, a function returning a operator's cost regarding its fields values. At this time, I wasn't thinking about short term memory.}
+  \item{apply, a function which uses a digit and generate a sequence by uncompressing this operator on it.}
+  \item{search, a function which tries to find current operator's application on a sequence.}
+\end{itemize}
+
+Given those methods, I defined three operators:
+\begin{itemize}
+  \item{A copy operator: using its predecessor's \textit{times}, copies given argument \textit{times} }
+  \item{An increment operator: increments and copy by one given argument \textit{times}. If this argument is an operator, it will copy it by incrementing its \textit{times} field. }
+  \item{A step operator: contains also a \textit{gap} argument and an \textit{operator} field, applies its operator by skipping as much elements as given by \textit{gap} on a list.}
+\end{itemize}
+
+The step operator was useful for this case:
+$$1\  2\  2\  3\  3\  3\  4\  4\  4\  4$$
+When compressed once using copy operator, it gave:
+$$(copy\ times(1))\ 1\ (copy\ times(2))\ 2\ (copy\ times(3))\ 3\ (copy\ times(4))\ 4$$
+Here, we can easily see that we have an increment on the digits and on the operators, but separated by one element each time. Using step operator, it gives:
+$$(step\ operator\ times(4)\ gap(1)\ operator(increment\ times(1)))\ 1\ 2\ 3\ 4$$
+The step operator will apply three times with a gap of one.
+As between each gap we only have one element, the increment operator in \textit{operator} field only applies once each time.
+The step operator will apply on the directly following element, the copy operator.
+A final compression would give:
+$$(step\ operator\ times(4)\ gap(1)\ operator(increment\ times(1)))\ (copy\ times(4))\ 4$$
+
+Speaking of complexity, if we count 1 for each operator plus recursive cost of all its arguments, the sequence $1\ 2\ 2\ 3\ 3\ 3\ 4\ 4\ 4\ 4$ will cost 23, where the compressed version costs 14.
+Hence, we can say that we have a compressed version.
+
+Copy and increment search were easy, I just had to compare current result with the next sequence's element.
+But for the step-operator, how can one determine the gap before searching?
+I tried each operator but with a gap of one.
+The problem was that it didn't used all the power of the step operator, but the search would cost a lot in an other way.
+And what a step operator applied on a step operator would mean?
+A real complex, not useful nor handy object actually.
+
+This solution displeased Jean-Louis Dessalles, because of this strange step-operator not really 'natural', and difficult to understand and to use.
+That is why he asked me to only use two operators: copy and increment.
+
+\section{Current solution}
+
+\section{Ways to continue}
 

### 2011-07-02 article.tex
Added previous solutions explanation in articles

@@
 $$(step\ operator\ times(4)\ gap(1)\ operator(increment\ times(1)))\ 1\ 2\ 3\ 4$$
-The step operator will apply three times with a gap of one.
-As between each gap we only have one element, the increment operator in \textit{operator} field only applies once each time.
+The step operator will apply three times with a gap of one. As between each gap we only have one element, the increment operator in \textit{operator} field only applies once each time.
 The step operator will apply on the directly following element, the copy operator.
 A final compression would give:
-$$(step\ operator\ times(4)\ gap(1)\ operator(increment\ times(1)))\ (copy\ times(4))\ 4$$
+$$(step\ operator\ times(4)\ gap(1)\ operator(increment\ times(1)))\ (increment\ times(4))\ 1$$
 
@@
 
-This solution displeased Jean-Louis Dessalles, because of this strange step-operator not really 'natural', and difficult to understand and to use.
+An other problem is that it is difficult to extend a list, what specific operator should we times-increment?
+On this particular example, it is the first operator of the list, but can we be so sure about it?
+And at first how can we be sure about the fact that a list \textit{is} extendible?
+
+This solution displeased Jean-Louis Dessalles, because of this strange step-operator not really 'natural', and its difficulties to understand and use.
 That is why he asked me to only use two operators: copy and increment.
+His point was that in the previous example, increment operator would have been applied at the same time on copy operator and on digits.
+That is why I should put the argument into the operator instead of leaving it on the list.
+Then, the increment operator would have seen a sequence of copy operator incrementing at the same time their \textit{times} and \textit{argument} fields.
+
+\subsection{Two operators with inelegant application}
+
+Now with this constraining consign, question was: "How can I apply different operators on the same object but on different fields?
+I imagined a solution that I found pretty ugly, but functional: copy-operator would now both now its \textit{argument} and \textit{times}.
+Increment-operator would moreover know where in his \textit{argument} it would apply: on its \textit{argument}, its \textit{times} or both.
+
+Here is an application on previous example:
+$$1\ 2\ 2\ 3\ 3\ 3\ 4\ 4\ 4\ 4$$
+$$(increment(1)(1))\ (increment(2)(2))\ (increment(3)(3))$$
+$$(increment(increment(1)(1))(3)(both))$$
+
+The \textit{where} field doesn't have any meaning when applying on a digit, and this is already a structural problem.
+This same field also doesn't have any meaning when applying on an increment-operator: it cannot apply on its argument because it is the contained increment-operator which takes care of that, and hence can only apply on its \textit{times}.
+
+With this solution, part of previous problems were solved: a list is only extendible if it can be reduced to one operator, and to extend it we only have to increment its \textit{times} field and then recursively decompress it.
+Furthermore, putting any operator in the \textit{operator} field of an increment-operator will always have a meaning, like we can imagine in this situation:
+$$1\ 1\ 1\ 2\ 1\ 1\ 2\ 1\ 2\ 3\ 1\ 1\ 2\ 1\ 2\ 3\ 1\ 2\ 3\ 4$$
+Compression would give:
+$$(increment(1)(1)(argument))\ (increment(1)(1)(argument))\ (increment(1)(2)(argument))\ (increment(1)(1)(argument))\ (increment(1)(2)(argument))\ (increment(1)(3)(argument))\ (increment(1)(1)(argument))\ (increment(1)(2)(argument))\ (increment(1)(3)(argument))\ (increment(1)(4)(argument))$$
+An other time would give:
+$$(increment(increment(1)(1)(argument))(1)(times))\ (increment(increment(1)(1)(argument))(2)(times))\ (increment(increment(1)(1)(argument))(3)(times))\ (increment(increment(1)(1)(argument))(4)(times))$$
+And a last one:
+$$(increment(increment(increment(1)(1)(argument))(1)(times))(4)(times))$$
+
+This solution is findable, putting apart the complexity problem (see below), and a huge problem which is at second iteration, how did he know that increment applied once applied only on times and not something else?
+I choose 'times' because it has hence be able to compress a last time given that all increment operators applied on 'times', but I had no right to do so.
+
+During a meeting with both Samuel Tardieu and Jean-Louis Dessalles, this solution worked pretty well, putting apart some complexity problems: sometimes 'good' -read 'expected'- solutions were not kept because they costed more than uncompressed sequence.
+For example, with $1\ 2\ 2\ 3\ 3\ 4$, the program considered three increments of two times in array, but rejected it.
+For the 'dirty' where-to-apply solution, Samuel cleverly suggested that instead of a restrictive three-choices field, I should use a indexes list which could also handle deepness which could indicate where the increment-operator should apply.
+This is the solution I adopted and customized in my final version.
 

### 2011-07-02 article.tex
Added current solution in article

@@
 As a student at Télécom ParisTech, I chose to follow the 'Non-classic languages paradigms' course with Samuel Tardieu\cite{samuel}, while working on a free project with Jean-Louis Dessalles\cite{jld}.
-Mr.
-Dessalles suggested a project based on a Komolgorov's complexity problem: given a small sequence of digits, shapes or characters, I had to design a small program able to complete this list as well as an eight-years old children.
+Jean-Louis Dessalles suggested a project based on a Komolgorov's complexity problem: given a small sequence of digits, shapes or characters, I had to design a small program able to complete this list as well as an eight-years old children.
 \cite{starting_point}
@@
 
-Here is an application on previous example:
+Here is an application on previous example (first parenthesis contain \textit{argument} and second \textit{times}):
 $$1\ 2\ 2\ 3\ 3\ 3\ 4\ 4\ 4\ 4$$
@@
 With this solution, part of previous problems were solved: a list is only extendible if it can be reduced to one operator, and to extend it we only have to increment its \textit{times} field and then recursively decompress it.
+\label{once_example}
 Furthermore, putting any operator in the \textit{operator} field of an increment-operator will always have a meaning, like we can imagine in this situation:
@@
 Compression would give:
-$$(increment(1)(1)(argument))\ (increment(1)(1)(argument))\ (increment(1)(2)(argument))\ (increment(1)(1)(argument))\ (increment(1)(2)(argument))\ (increment(1)(3)(argument))\ (increment(1)(1)(argument))\ (increment(1)(2)(argument))\ (increment(1)(3)(argument))\ (increment(1)(4)(argument))$$
+$$(increment(1)(1)(arg))$$
+$$(increment(1)(1)(arg))\ (increment(1)(2)(arg))$$
+$$(increment(1)(1)(arg))\ (increment(1)(2)(arg))\ (increment(1)(3)(arg))$$
+$$(increment(1)(1)(arg))\ (increment(1)(2)(arg))\ (increment(1)(3)(arg))\ (increment(1)(4)(arg))$$
 An other time would give:
-$$(increment(increment(1)(1)(argument))(1)(times))\ (increment(increment(1)(1)(argument))(2)(times))\ (increment(increment(1)(1)(argument))(3)(times))\ (increment(increment(1)(1)(argument))(4)(times))$$
+$$(increment(increment(1)(1)(arg))(1)(times))$$
+$$(increment(increment(1)(1)(arg))(2)(times))$$
+$$(increment(increment(1)(1)(arg))(3)(times))$$
+$$(increment(increment(1)(1)(arg))(4)(times))$$
 And a last one:
-$$(increment(increment(increment(1)(1)(argument))(1)(times))(4)(times))$$
+$$(increment(increment(increment(1)(1)(arg))(1)(times))(4)(times))$$
 
 This solution is findable, putting apart the complexity problem (see below), and a huge problem which is at second iteration, how did he know that increment applied once applied only on times and not something else?
-I choose 'times' because it has hence be able to compress a last time given that all increment operators applied on 'times', but I had no right to do so.
+I choose 'times' because it has hence been able to compress a last time given that all increment operators applied on 'times', but I had no right to do so.
 
@@
 For example, with $1\ 2\ 2\ 3\ 3\ 4$, the program considered three increments of two times in array, but rejected it.
-For the 'dirty' where-to-apply solution, Samuel cleverly suggested that instead of a restrictive three-choices field, I should use a indexes list which could also handle deepness which could indicate where the increment-operator should apply.
+For the 'dirty' where-to-apply solution, Samuel cleverly suggested that instead of a restrictive three-choices field, I should use a indexes list which could also handle deepness indicating where the increment-operator should apply.
 This is the solution I adopted and customized in my final version.
@@
 
+Current solution is axed on Factor's suffixed way: an operator is represented by a letter, $C$ for copy and $I$ for increment, and applies on a specified number of arguments \textit{before} it.
+Elements in a compressed sequence are only compressed sequences, digits or operators letters.
+Customized indexed work this way: increment operators own in their \textit{where} field a sequence of digits, which are indexes representing an element's absolute position in extended sequence.
+For example, let us consider the following sequence:
+$$\{\ 0\ 1\ \{\ 2\ \{\ 3\ 4\ \}\ 5\ \{\ 6\ \}\ \}\ 7\ \{\ 8\ \}\ 9\ \}$$
+Digits represent each element's index.
+Hence, any deepness level can be reached, and no need is to recall structural information with for example tree indexes, in which case element 4 would be accessed with 3.1.1 instead of just 4.
+This notation is easier to manipulate and resulting \textit{where} sequence may even be compressed!
+Jean-Louis Dessalles wasn't really satisfied by this index solution: it wouldn't respect Kantian structural form of the model (we should be able to manipulate shapes or vegetables as well) and structure is absolutely not represented using it.
+He suggested the use of masks, more 'natural' and compressed than my indexes notation, but it doesn't solve the structure's respect problem and is actually in bijection with my system (as it is more important to act simply and 'humanly' than saving RAM, we can neglect the compression difference).
+
+Here is an example of using this system on our favorite example:
+$$1\ 2\ 2\ 3\ 3\ 3\ 4\ 4\ 4\ 4$$
+$$1\ 1\ C\ 2\ 2\ C\ 3\ 3\ C\ 4\ 4\ C$$
+$${\ 1\ 1\ C\ }\ {\ 0\ 1\ }\ 4\ I$$
+We only have one operator left, just with its arguments.
+We increment its \textit{times} field:
+$${\ 1\ 1\ C\ }\ {\ 0\ 1\ }\ 5\ I$$
+And decompress it to obtain logical extension:
+$$1\ 1\ C\ 2\ 2\ C\ 3\ 3\ C\ 4\ 4\ C\ 5\ 5\ C$$
+$$1\ 2\ 2\ 3\ 3\ 3\ 4\ 4\ 4\ 4\ 5\ 5\ 5\ 5\ 5$$
+
+\section{Backtracking with Factor}
+
+Let us see deeper how search algorithm works, using Factor's backtracking power.
+TODO
+
 \section{Ways to continue}
+
+\subsection{Once applied increment operators}
+
+As we saw before, when we find an increment operator used only once (\textit{times} = 1), its \textit{where} field doesn't mean anything, as when decompressed, \textit{argument} is only extracted, $I$, \textit{times} and \textit{where} being simply removed form the sequence.
+Normally, such a representation should be rejected because it trivially is less compressed than just writing \textit{argument} as is.
+It may be useful in 'Dirty' solution example (\ref{once_example}):
+$$1\ 1\ 1\ 2\ 1\ 1\ 2\ 1\ 2\ 3\ 1\ 1\ 2\ 1\ 2\ 3\ 1\ 2\ 3\ 4$$
+At first
 
@@
 \bibitem{samuel} Samuel Tardieu's website: \url{http://www.rfc1149.net/}
-\bibitem{jld} Jean Louis Dessalles' website: \url{http://perso.telecom-paristech.fr/~jld/}
+\bibitem{jld} Jean-Louis Dessalles' website: \url{http://perso.telecom-paristech.fr/~jld/}
 \bibitem{starting_point} A starting point: \url{http://icc.enst.fr/PLC/Learn.html}, section Complexity

### 2011-07-02 article.tex
Added once used problem in article

@@
 \usepackage{hyperref}
+\usepackage{color}
 
@@
 With this solution, part of previous problems were solved: a list is only extendible if it can be reduced to one operator, and to extend it we only have to increment its \textit{times} field and then recursively decompress it.
-\label{once_example}
 Furthermore, putting any operator in the \textit{operator} field of an increment-operator will always have a meaning, like we can imagine in this situation:
 $$1\ 1\ 1\ 2\ 1\ 1\ 2\ 1\ 2\ 3\ 1\ 1\ 2\ 1\ 2\ 3\ 1\ 2\ 3\ 4$$
-Compression would give:
+Compression would give (sequence is cut for better understanding):
 $$(increment(1)(1)(arg))$$
@@
 $$(increment(1)(1)(arg))\ (increment(1)(2)(arg))\ (increment(1)(3)(arg))\ (increment(1)(4)(arg))$$
+
 An other time would give:
@@
 Digits represent each element's index.
-Hence, any deepness level can be reached, and no need is to recall structural information with for example tree indexes, in which case element 4 would be accessed with 3.1.1 instead of just 4.
+Hence, any deepness level can be reached, and no need is to recall structural information with for example tree indexes, in which case element 4 would be accessed with 2.1.1 instead of just 4.
 This notation is easier to manipulate and resulting \textit{where} sequence may even be compressed!
-Jean-Louis Dessalles wasn't really satisfied by this index solution: it wouldn't respect Kantian structural form of the model (we should be able to manipulate shapes or vegetables as well) and structure is absolutely not represented using it.
+Jean-Louis Dessalles wasn't really satisfied by this index solution: it wouldn't respect Kantian structural form of the model (we should be able to manipulate shapes or vegetables as well and using them all along the model) and structure is absolutely not represented using it.
 He suggested the use of masks, more 'natural' and compressed than my indexes notation, but it doesn't solve the structure's respect problem and is actually in bijection with my system (as it is more important to act simply and 'humanly' than saving RAM, we can neglect the compression difference).
+
+For easier representation, an \textit{argument} or a \textit{where} field reduced to only one argument is not contained into a sequence, but inserted as is.
 
@@
 $$1\ 1\ C\ 2\ 2\ C\ 3\ 3\ C\ 4\ 4\ C$$
-$${\ 1\ 1\ C\ }\ {\ 0\ 1\ }\ 4\ I$$
+$$\{\ 1\ 1\ C\ \}\ \{\ 0\ 1\ \}\ 4\ I$$
 We only have one operator left, just with its arguments.
 We increment its \textit{times} field:
-$${\ 1\ 1\ C\ }\ {\ 0\ 1\ }\ 5\ I$$
+$$\{\ 1\ 1\ C\ \}\ \{\ 0\ 1\ \}\ 5\ I$$
 And decompress it to obtain logical extension:
@@
 As we saw before, when we find an increment operator used only once (\textit{times} = 1), its \textit{where} field doesn't mean anything, as when decompressed, \textit{argument} is only extracted, $I$, \textit{times} and \textit{where} being simply removed form the sequence.
-Normally, such a representation should be rejected because it trivially is less compressed than just writing \textit{argument} as is.
-It may be useful in 'Dirty' solution example (\ref{once_example}):
+Normally, such a representation should be rejected because it is trivially less compressed than just writing \textit{argument} as is.
+It may be useful this example :
 $$1\ 1\ 1\ 2\ 1\ 1\ 2\ 1\ 2\ 3\ 1\ 1\ 2\ 1\ 2\ 3\ 1\ 2\ 3\ 4$$
-At first
+Let compress it using our method (sequence is cut for better understanding):
+$$1\ 0\ 1\ I$$
+$$1\ 0\ 1\ I\ 1\ 0\ 2\ I$$
+$$1\ 0\ 1\ I\ 1\ 0\ 2\ I\ 1\ 0\ 3$$
+$$I\ 1\ 0\ 1\ I\ 1\ 0\ 2\ I\ 1\ 0\ 3\ I\ 1\ 0\ 4\ I$$
+
+This is of course one over a lot of obtainable solutions, but it is findable by our process so we have the right to consider it.
+Here we will make an 'error' which will cost us the solution:
+$$\{\ 1\ 0\ 1\ I\ \}\ \textcolor{red}{0}\ 1\ I$$
+$$\{\ 1\ 0\ 1\ I\ \}\ \textcolor{green}{2}\ 2\ I$$
+$$\{\ 1\ 0\ 1\ I\ \}\ \textcolor{green}{2}\ 3\ I$$
+$$\{\ 1\ 0\ 1\ I\ \}\ \textcolor{green}{2}\ 4\ I$$
+Now, we would like to obtain
+$$\{\ \{\ 1\ 0\ 1\ I\ \}\ \{\ 0\ 2\ \}\ 3\ I\ \}\ 6\ 4\ I$$
+but our program will \textcolor{red}{fail} when comparing $0$ and $2$.
+A solution would be to use a 'joker', like Factor's f in order to warn when compared with an other value that this value has not been defined yet.
+For now, the program is not able to solve this problem without removing the first lonely $1$.
+
+\subsection{Masks and indexes}
+
+\subsection{Short memory}
 

### 2011-07-02 article.tex
Added conclusion in article

@@
 As we saw before, when we find an increment operator used only once (\textit{times} = 1), its \textit{where} field doesn't mean anything, as when decompressed, \textit{argument} is only extracted, $I$, \textit{times} and \textit{where} being simply removed form the sequence.
+
 Normally, such a representation should be rejected because it is trivially less compressed than just writing \textit{argument} as is.
@@
 but our program will \textcolor{red}{fail} when comparing $0$ and $2$.
-A solution would be to use a 'joker', like Factor's f in order to warn when compared with an other value that this value has not been defined yet.
+
+A solution would be to use a 'joker', like Factor's $f$ in order to warn when compared with an other value that this value has not been defined yet.
 For now, the program is not able to solve this problem without removing the first lonely $1$.
@@
 
+An other way to improve the program is to solve the problem how to indicate where to apply the increment-operator in a natural, compressed and Kantian way.
+
+This problem has been there since the beginning of the project, and even if a lots of plus or minus elegant solutions has been found, a lot of work is to been done on this subject.
+
 \subsection{Short memory}
+
+As explained before, the use of short memory is not reliable and quite difficult to implement.
+Even though a whole implementation has been done, it is not used in final version because of its random characteristic.
+
+An improvement would be to find a way to use it, while keeping this program's reliability and power.
+
+\section{Conclusion}
+
+This project has been an excellent way to use at a project scale a new and powerful language as Factor.
+
+It revealed itself difficult to use at first but incredibly efficient for this particular subject.
+The project itself proved to be harder than expected, because of its 'human' closely restriction.
+It has been a opportunity to consider and try to bring solutions in a little known field.
+
+This was an enriching experience and it worthed spending time working on it.
 

### 2011-07-02 article.tex
Corrected a lot before writing last part

@@
 
-Using this complexity, one could define $1\ 2\ 2\ 3\ 3\ 3$ as 'count from one and repeat each number as much as itself', which is really easier to understand, memorize and extend for an human than a random sequence, like a telephone or a credit card number.
+Using this complexity, one could define $1\ 2\ 2\ 3\ 3\ 3$ as 'count from one and repeat each number as much as itself', which is really easier to understand, memorize and extend for an human than a random sequence, like a telephone or credit card number.
 We will explore different ways to represent and manipulate such informations.
@@
 An other way to compute a list's complexity would be to use \textit{short term memory}, a list or tree containing last used elements.
-An access to one of those elements would be its address for example binary coded.
+An access to one of those elements would be its binary coded address for example.
 This model is easily explainable considering that a human, if he was able to solve a problem using a specific operator, will naturally try it first when confronted to a new problem.
@@
 
-\section{Tentatives}
+\section{Attempts}
 
@@
 \begin{itemize}
-  \item{cost, a function returning a operator's cost regarding its fields values. At this time, I wasn't thinking about short term memory.}
-  \item{apply, a function which uses a digit and generate a sequence by uncompressing this operator on it.}
+  \item{cost, a function returning an operator's cost regarding its fields values.}
+  \item{apply, a function which uses a sequence and generate a sequence by uncompressing this operator on it (often only using its first element).}
   \item{search, a function which tries to find current operator's application on a sequence.}
@@
 \begin{itemize}
-  \item{A copy operator: using its predecessor's \textit{times}, copies given argument \textit{times} }
-  \item{An increment operator: increments and copy by one given argument \textit{times}. If this argument is an operator, it will copy it by incrementing its \textit{times} field. }
-  \item{A step operator: contains also a \textit{gap} argument and an \textit{operator} field, applies its operator by skipping as much elements as given by \textit{gap} on a list.}
+  \item{A copy operator: using its predecessor's \textit{times} field, copies given argument \textit{times} times. }
+  \item{An increment operator: increments and copy given argument \textit{times} times. If this argument is an operator, it will copy it by incrementing its \textit{times} field. }
+  \item{A step operator: also contains a \textit{gap} argument and an \textit{operator} field, applies its operator by skipping as much elements as given by \textit{gap} on a list.}
 \end{itemize}
@@
 A final compression would give:
-$$(step\ operator\ times(4)\ gap(1)\ operator(increment\ times(1)))\ (increment\ times(4))\ 1$$
+$$(step\ operator\ times(4)\ gap(1)\ operator(increment\ times(1)))$$
+$$(increment\ times(4))\ 1$$
 
@@
 
-This solution displeased Jean-Louis Dessalles, because of this strange step-operator not really 'natural', and its difficulties to understand and use.
+This solution displeased Jean-Louis Dessalles, because of this strange step-operator not really 'natural', and its difficulties to be understood and used.
 That is why he asked me to only use two operators: copy and increment.
-His point was that in the previous example, increment operator would have been applied at the same time on copy operator and on digits.
+His point was that in the previous example, increment operator should have been applied at the same time on copy operator and on digits.
 That is why I should put the argument into the operator instead of leaving it on the list.
@@
 I imagined a solution that I found pretty ugly, but functional: copy-operator would now both now its \textit{argument} and \textit{times}.
-Increment-operator would moreover know where in his \textit{argument} it would apply: on its \textit{argument}, its \textit{times} or both.
+Increment-operator would inherit from copy-operator and moreover know where in his \textit{argument} it would apply: on its \textit{argument}, its \textit{times} or both.
+This information was stored on a \textit{where} field.
 
-Here is an application on previous example (first parenthesis contain \textit{argument} and second \textit{times}):
+Here is an application on previous example (first parenthesis contain \textit{argument}, second \textit{times} and last \textit{where}):
 $$1\ 2\ 2\ 3\ 3\ 3\ 4\ 4\ 4\ 4$$
-$$(increment(1)(1))\ (increment(2)(2))\ (increment(3)(3))$$
-$$(increment(increment(1)(1))(3)(both))$$
+$$(increment(1)(1)(arg))\ (increment(2)(2)(arg))\ (increment(3)(3)(arg))$$
+$$(increment(increment(1)(1)(arg))(3)(both))$$
 
@@
 This solution is findable, putting apart the complexity problem (see below), and a huge problem which is at second iteration, how did he know that increment applied once applied only on times and not something else?
-I choose 'times' because it has hence been able to compress a last time given that all increment operators applied on 'times', but I had no right to do so.
+I chose 'times' because it has hence been able to compress a last time given that all increment operators applied on 'times', but I had no right to do so.
 
-During a meeting with both Samuel Tardieu and Jean-Louis Dessalles, this solution worked pretty well, putting apart some complexity problems: sometimes 'good' -read 'expected'- solutions were not kept because they costed more than uncompressed sequence.
+During a meeting with both Samuel Tardieu and Jean-Louis Dessalles, this solution worked pretty well, putting apart some complexity problems: sometimes 'good' (think 'expected') solutions were not kept because they costed more than uncompressed sequence.
 For example, with $1\ 2\ 2\ 3\ 3\ 4$, the program considered three increments of two times in array, but rejected it.
@@
 Elements in a compressed sequence are only compressed sequences, digits or operators letters.
-Customized indexed work this way: increment operators own in their \textit{where} field a sequence of digits, which are indexes representing an element's absolute position in extended sequence.
+Customized indexes work this way: increment operators own in their \textit{where} field a sequence of digits, which are indexes representing an element's absolute position in extended \textit{argument}.
 For example, let us consider the following sequence:
-$$\{\ 0\ 1\ \{\ 2\ \{\ 3\ 4\ \}\ 5\ \{\ 6\ \}\ \}\ 7\ \{\ 8\ \}\ 9\ \}$$
-Digits represent each element's index.
-Hence, any deepness level can be reached, and no need is to recall structural information with for example tree indexes, in which case element 4 would be accessed with 2.1.1 instead of just 4.
+$$\{\ a_0\ a_1\ \{\ a_2\ \{\ a_3\ a_4\ \}\ a_5\ \{\ a_6\ \}\ \}\ a_7\ \{\ a_8\ \}\ a_9\ \}$$
+Indexes are used extended indexes.
+Hence, any deepness level can be reached, and no need is to recall structural information, like for example with tree indexes, in which case element $a_4$ would be accessed with $2.1.1$ instead of $4$.
 This notation is easier to manipulate and resulting \textit{where} sequence may even be compressed!
+
 Jean-Louis Dessalles wasn't really satisfied by this index solution: it wouldn't respect Kantian structural form of the model (we should be able to manipulate shapes or vegetables as well and using them all along the model) and structure is absolutely not represented using it.
@@
 
-For easier representation, an \textit{argument} or a \textit{where} field reduced to only one argument is not contained into a sequence, but inserted as is.
+For easier representation, an \textit{argument} or a \textit{where} field reduced to only one element is not contained into a sequence, but inserted as is.
+
+We also define operators' arguments order:
+\begin{itemize}
+  \item{$WHAT\ TIMES\ C$}
+  \item{$WHAT\ WHERE\ TIMES\ I$}
+\end{itemize}
 
@@
 
-As we saw before, when we find an increment operator used only once (\textit{times} = 1), its \textit{where} field doesn't mean anything, as when decompressed, \textit{argument} is only extracted, $I$, \textit{times} and \textit{where} being simply removed form the sequence.
+As we saw before, when we find an increment operator used only once (\textit{times} = 1), its \textit{where} field doesn't mean anything, as when decompressed, \textit{argument} is only extracted, $I$, \textit{times} and \textit{where} fields being simply removed from the sequence.
 
@@
 Now, we would like to obtain
-$$\{\ \{\ 1\ 0\ 1\ I\ \}\ \{\ 0\ 2\ \}\ 3\ I\ \}\ 6\ 4\ I$$
+$$\{\ \{\ 1\ 0\ 1\ I\ \}\ 2\ 1\ I\ \}\ 6\ 4\ I$$
 but our program will \textcolor{red}{fail} when comparing $0$ and $2$.
@@
 
-An other way to improve the program is to solve the problem how to indicate where to apply the increment-operator in a natural, compressed and Kantian way.
+An other way to improve the program is to solve the 'how to indicate where to apply the increment-operator in a natural, compressed and Kantian way' problem.
 
-This problem has been there since the beginning of the project, and even if a lots of plus or minus elegant solutions has been found, a lot of work is to been done on this subject.
+It has been there since the beginning of the project, and even if a lots of plus or minus elegant solutions have been found, a lot of work is to been done on this subject.
 
-\subsection{Short memory}
+\subsection{Short term memory}
 
 As explained before, the use of short memory is not reliable and quite difficult to implement.
-Even though a whole implementation has been done, it is not used in final version because of its random characteristic.
+Even though a whole implementation has been done, it is not used in final version because of its random behaviour.
 
@@
 It revealed itself difficult to use at first but incredibly efficient for this particular subject.
-The project itself proved to be harder than expected, because of its 'human' closely restriction.
+The project itself proved to be harder than expected, because of its 'human' restriction.
 It has been a opportunity to consider and try to bring solutions in a little known field.

### 2011-07-02 article.tex
Article is ready for correction

@@
 
+For results purpose, $C$ and $I$ words don't cost anything.
+
 We also define operators' arguments order:
@@
 Let us see deeper how search algorithm works, using Factor's backtracking power.
-TODO
+
+\subsection{\textcolor{green}{amb} and \textcolor{red}{fail}}
+
+Using continuations in factor, we can use \textcolor{green}{amb} to test all elements in a sequence.
+When \textcolor{red}{fail} is called, the program comes back to the last \textcolor{green}{amb} call and tries its next element.
+If no element is left, this level is abandoned and the previous one is considered.
+This system, quite close to Prolog's one, is useful to try possibilities at different levels, and backtrack in case of failure to the next possibility.
+
+\subsection{Search order}
+
+As it is able to complete not complete sequences, the program will first try to remove from 0 to length minus 1 elements.
+At each removal, it will check if when extended the resulting sequence contains the initial one and \textcolor{red}{fail} otherwise.
+
+If nothing is found, it will extract the given sequence's elements in a such way that all elements are present only once, and ordered from the last found to the first one.
+The program will then try all combination with a adding length limit of the initial sequence's length.
+This part has a $n!$ complexity, but is rarely reached because it is easy to find a solution
+
+Those operation are two parallels \textcolor{green}{amb}.
+
+Given a sequence on which we would like to search, we try to compress it using several \textcolor{green}{amb}.
+
+At first, we try an operator, $C$ and then $I$.
+
+Given an operator, we decide a searching size.
+We will try from 1 up to the sequence's length.
+A size represents what is taken from a list in order to search on it.
+This parameter is important, for example to detect incrementation from an operator to another, like in the next section example.
+
+Once an operator and a size has been chosen, we compress the sequence from the left to the right by going as far as possible and appending result to previous results until the rest is empty
+(if the rest is not long enough to be taken \textit{size} elements, the program will \textcolor{red}{fail}.
+
+Once a list has been compressed, it is rejected if all found operators are only applied once.
+Its complexity is then compared to initial sequence's one, and the best one is kept (if complexities are equal, the previous sequence is kept and we \textcolor{red}{fail}).
+
+If we were able to compress until we have got only an operator and its arguments (3 for $C$ and 4 for $I$), we check if arguments are coherent and finally extend if so, by increasing its times and then uncompress the final sequence.
+
+I also implemented a way to look after \textit{all} solutions, but as the adding part has a $n!$ complexity, this way takes a very long time to return.
+
+For any implementation considering, see the program documentation as explained in my git repository README.
+I spend quite a long time writing it as exhaustive as possible, so that a good comprehension of the program is possible.
 

### 2011-07-02 article.tex
Corrected a little bit

--- 2011-07-02 article.tex
@@
 
-The main purpose of this project is to apply Kolmogorov theory on the given list in order to compress it in a optimal and human way, so that we will then be able to extend that list using found compression process.
+The main goal of this project is to apply Kolmogorov theory on the given list in order to compress it in a optimal and human way, so that we will then be able to extend that list using found compression process.
 On the 'Non-classic languages paradigms' course, we learned small spread languages as Haskel, Scala or Factor, and we were also supposed to perform a small implementation project using one of those languages.
 
-Factor\cite{factor} is a quite memory-close language, able to perform back-tracking as well as Prolog using continuations and working on a stack, like a logical sequence.
-Its powerful and non-standard architecture make him a very interesting language to work on, and that is why I chose to use it to implement my project.
+Factor\cite{factor} is a quite memory-close language, able to perform backtracking as well as Prolog using continuations and working on a stack, like a logical sequence.
+Its powerful and non-standard architecture makes it a very interesting language to work on, and this is why I chose to use it to implement my project.
 
@@
 
-Humans' capability to compress and understand structures always fascinated computer sciences researchers.
-Humans are able to perfectly perform tasks as recognizing a person's face, understand a language or, in our scope of interest, understand and complete a list of digits, alphabetics or shapes.
-Those tasks are very difficult to efficiently complete for machines, even using the most powerful computers.
-That is why a huge domain of research still exists in that field, always in the same goal: give machines more and more of our 'human intelligence'.
+Humans capabilities to compress and understand structures have always fascinated computer sciences researchers.
+Humans are able to perform perfectly tasks as recognizing a person's face, understand a language or, in our scope of interest, understand and complete a list of digits, alphabetics or shapes.
+Those tasks are very difficult to be completed efficiently by machines, even using the most powerful computers.
+That is why a huge domain of research still exists on that subject, always with the same goal: give machines more and more of our "human intelligence".
 
@@
 $$1\ 2\ 2\ 3\ 3\ 3$$
-Any eight-years old children would easily suggest that a good continuation of this sequence would be:
+Any eight-years old children would easily suggests that a good continuation of this sequence would be:
 $$1\ 2\ 2\ 3\ 3\ 3\ 4\ 4\ 4\ 4$$
 But how can one be so sure about it?
-This is where we can introduce the notion of 'complexity', and more especially Kolmogorov's one:
+This is where we can introduce the notion of "complexity", and more especially Kolmogorov's one:
 
@@
 
-In other words, this complexity has the particularity to highly depends of using person, and is therefore really difficult to use inside a program.
+In other words, this complexity has the particularity to highly depends of the user, and is moreover really difficult to use it inside a program.
 
-Using this complexity, one could define $1\ 2\ 2\ 3\ 3\ 3$ as 'count from one and repeat each number as much as itself', which is really easier to understand, memorize and extend for an human than a random sequence, like a telephone or credit card number.
+Using this complexity, someone could define $1\ 2\ 2\ 3\ 3\ 3$ as "count from one and repeat each number as much as itself", which is really easier to understand, memorize and extend for an human than a random sequence, like a telephone or credit card number.
 We will explore different ways to represent and manipulate such informations.
@@
 An other way to compute a list's complexity would be to use \textit{short term memory}, a list or tree containing last used elements.
-An access to one of those elements would be its binary coded address for example.
-This model is easily explainable considering that a human, if he was able to solve a problem using a specific operator, will naturally try it first when confronted to a new problem.
+An access to one of those elements would be its binary coded address, for example.
+This model is easily explainable considering that a human, if he was able to solve a problem using a specific operator, will naturally try this operator first when confronted to a new problem.
 This list is implemented but not used because of its unpredictable character.
 
-That is why in present version a standard \textit{binary coding} is used to compute a list's complexity, with 0 costing 0.
+That is why in the present version a standard \textit{binary coding} is used to compute a list's complexity, with 0 costing 0.
 
@@
 
-At first, I thought about using Factor's \textit{tuples}, special sequences of fields easily sharable between descendants, like standard \textit{Object Oriented Programming}.
+At first, I thought about using Factor's \textit{tuples}, special sequences of easily sharable between descendants fields, like standard \textit{Object Oriented Programming}.
 
@@
   \item{cost, a function returning an operator's cost regarding its fields values.}
-  \item{apply, a function which uses a sequence and generate a sequence by uncompressing this operator on it (often only using its first element).}
+  \item{apply, a function which uses a sequence and generate a sequence by uncompressing this operator on it (often using only its first element).}
   \item{search, a function which tries to find current operator's application on a sequence.}
@@
   \item{A copy operator: using its predecessor's \textit{times} field, copies given argument \textit{times} times. }
-  \item{An increment operator: increments and copy given argument \textit{times} times. If this argument is an operator, it will copy it by incrementing its \textit{times} field. }
+  \item{
+    An increment operator: increments and copy given argument \textit{times} times.
+    If this argument is an operator, it will copy it by incrementing its \textit{times} field. }
   \item{A step operator: also contains a \textit{gap} argument and an \textit{operator} field, applies its operator by skipping as much elements as given by \textit{gap} on a list.}
@@
 $$(copy\ times(1))\ 1\ (copy\ times(2))\ 2\ (copy\ times(3))\ 3\ (copy\ times(4))\ 4$$
-Here, we can easily see that we have an increment on the digits and on the operators, but separated by one element each time. Using step operator, it gives:
+Here, we can easily see that we have an increment on the digits and on the operators, but separated by one element each time.
+Using step operator, it gives:
 $$(step\ operator\ times(4)\ gap(1)\ operator(increment\ times(1)))\ 1\ 2\ 3\ 4$$
-The step operator will apply three times with a gap of one. As between each gap we only have one element, the increment operator in \textit{operator} field only applies once each time.
+The step operator will apply three times with a gap of one.
+As between each gap we only have one element, the increment operator in \textit{operator} field only applies once each time.
 The step operator will apply on the directly following element, the copy operator.
@@
 Copy and increment search were easy, I just had to compare current result with the next sequence's element.
-But for the step-operator, how can one determine the gap before searching?
+But for the step-operator, how to determine the gap before searching?
 I tried each operator but with a gap of one.
-The problem was that it didn't used all the power of the step operator, but the search would cost a lot in an other way.
-And what a step operator applied on a step operator would mean?
+The problem was that it didn't used all the power of the step operator, but the search would cost a lot in another way.
+And what does a step operator applied on a step operator would mean?
 A real complex, not useful nor handy object actually.
 
-An other problem is that it is difficult to extend a list, what specific operator should we times-increment?
-On this particular example, it is the first operator of the list, but can we be so sure about it?
-And at first how can we be sure about the fact that a list \textit{is} extendible?
+An other problem is that it is difficult to extend a list, what specific operator should we "times-increment"?
+On this particular example, it is the first operator of the list, but can we be sure about it?
+And foremost, how can we be sure about the fact that a list \textit{is} extendible?
 
-This solution displeased Jean-Louis Dessalles, because of this strange step-operator not really 'natural', and its difficulties to be understood and used.
+This solution displeased Jean-Louis Dessalles, because of this not really "natural" strange step-operator, and its difficulties to be understood and used.
 That is why he asked me to only use two operators: copy and increment.
 His point was that in the previous example, increment operator should have been applied at the same time on copy operator and on digits.
-That is why I should put the argument into the operator instead of leaving it on the list.
+Therefore, I should put the argument into the operator instead of leaving it on the list.
 Then, the increment operator would have seen a sequence of copy operator incrementing at the same time their \textit{times} and \textit{argument} fields.
@@
 
-Now with this constraining consign, question was: "How can I apply different operators on the same object but on different fields?
-I imagined a solution that I found pretty ugly, but functional: copy-operator would now both now its \textit{argument} and \textit{times}.
+Now with this constraining consign, the question was: "How can I apply different operators on the same object but on different fields?"
+I imagined a solution that I found pretty ugly, but functional: copy-operator would now both know its \textit{argument} and \textit{times}.
 Increment-operator would inherit from copy-operator and moreover know where in his \textit{argument} it would apply: on its \textit{argument}, its \textit{times} or both.
@@
 $$1\ 1\ 1\ 2\ 1\ 1\ 2\ 1\ 2\ 3\ 1\ 1\ 2\ 1\ 2\ 3\ 1\ 2\ 3\ 4$$
-Compression would give (sequence is cut for better understanding):
+Compression would give (sequence has been cut for better understanding):
 $$(increment(1)(1)(arg))$$
@@
 
-This solution is findable, putting apart the complexity problem (see below), and a huge problem which is at second iteration, how did he know that increment applied once applied only on times and not something else?
-I chose 'times' because it has hence been able to compress a last time given that all increment operators applied on 'times', but I had no right to do so.
+This solution is findable, putting apart the complexity problem (see below), and a huge problem which is at second iteration, how did it know that increment applied once applied only on \textit{times} and not something else?
+I chose \textit{times} because it has been able to compress a last time, given that all increment operators applied on \textit{times}, but I had no right to do so.
 
-During a meeting with both Samuel Tardieu and Jean-Louis Dessalles, this solution worked pretty well, putting apart some complexity problems: sometimes 'good' (think 'expected') solutions were not kept because they costed more than uncompressed sequence.
-For example, with $1\ 2\ 2\ 3\ 3\ 4$, the program considered three increments of two times in array, but rejected it.
-For the 'dirty' where-to-apply solution, Samuel cleverly suggested that instead of a restrictive three-choices field, I should use a indexes list which could also handle deepness indicating where the increment-operator should apply.
+During a meeting with both Samuel Tardieu and Jean-Louis Dessalles, this solution worked pretty well, putting apart some complexity problems: sometimes "good" (think "expected") solutions were not kept because they costed more than uncompressed sequence.
+For example, with $1\ 2\ 2\ 3\ 3\ 4$, the program considered three increments of two times in a row, but rejected it.
+For the "dirty" where-to-apply solution, Samuel cleverly suggested that instead of a restrictive three-choices field, I should use a indexes list which could also handle deepness, indicating where the increment-operator should apply.
 This is the solution I adopted and customized in my final version.
@@
 
-Current solution is axed on Factor's suffixed way: an operator is represented by a letter, $C$ for copy and $I$ for increment, and applies on a specified number of arguments \textit{before} it.
+Current solution is axed on Factor's suffixed way: an operator is represented by a letter, $C$ for copy or $I$ for increment, and applies on a specified number of arguments BEFORE it.
 Elements in a compressed sequence are only compressed sequences, digits or operators letters.
-Customized indexes work this way: increment operators own in their \textit{where} field a sequence of digits, which are indexes representing an element's absolute position in extended \textit{argument}.
+Customized indexes work that way: increment operators own in their \textit{where} field a sequence of digits, which are indexes representing an element's absolute position in extended \textit{argument}.
 For example, let us consider the following sequence:
 $$\{\ a_0\ a_1\ \{\ a_2\ \{\ a_3\ a_4\ \}\ a_5\ \{\ a_6\ \}\ \}\ a_7\ \{\ a_8\ \}\ a_9\ \}$$
-Indexes are used extended indexes.
-Hence, any deepness level can be reached, and no need is to recall structural information, like for example with tree indexes, in which case element $a_4$ would be accessed with $2.1.1$ instead of $4$.
+Indexes are extended indexes.
+Hence, any deepness level can be reached, and there is no need to recall structural information, like with tree indexes, in which case element $a_4$ would be accessed with $2.1.1$ instead of $4$.
 This notation is easier to manipulate and resulting \textit{where} sequence may even be compressed!
 
-Jean-Louis Dessalles wasn't really satisfied by this index solution: it wouldn't respect Kantian structural form of the model (we should be able to manipulate shapes or vegetables as well and using them all along the model) and structure is absolutely not represented using it.
-He suggested the use of masks, more 'natural' and compressed than my indexes notation, but it doesn't solve the structure's respect problem and is actually in bijection with my system (as it is more important to act simply and 'humanly' than saving RAM, we can neglect the compression difference).
+Jean-Louis Dessalles wasn't really satisfied by this index solution: it wouldn't respect Kantian structural form of the model
+(we should be able to manipulate shapes or vegetables as well and using them all along the model) and the structure is absolutely not represented using it.
+He suggested the use of masks, more "natural" and compressed than my indexes notation, but it doesn't solve the structure's respect problem and it is actually in bijection with my system
+(as it is more important to act simply and 'humanly' than saving RAM, we can neglect the compression difference).
 
 For easier representation, an \textit{argument} or a \textit{where} field reduced to only one element is not contained into a sequence, but inserted as is.
+
+For results purpose, $C$ and $I$ words don't cost anything.
 
@@
 
-Here is an example of using this system on our favorite example:
+Here is an example of the use of this system on our favorite example:
 $$1\ 2\ 2\ 3\ 3\ 3\ 4\ 4\ 4\ 4$$
@@
 
-Let us see deeper how search algorithm works, using Factor's backtracking power.
-TODO
+Let us see closer how does search algorithm work, using Factor's backtracking power.
+
+\subsection{\textcolor{green}{amb} and \textcolor{red}{fail}}
+
+Using continuations in factor, we can use \textcolor{green}{amb} to test all elements in a sequence.
+When \textcolor{red}{fail} is called, the program comes back to the last \textcolor{green}{amb} call and tries its next element.
+If there is no element left, this level is abandoned and the previous one is considered.
+This system, quite close to Prolog's one, is useful to try possibilities at different levels, and backtrack in case of failure to the next possibility.
+
+\subsection{Search order}
+
+As it is able to complete incomplete sequences, the program will first try to remove from 0 to the length minus 2 elements.
+At each removal, it will check if when extended the resulting sequence contains the initial one and \textcolor{red}{fail} otherwise.
+
+If nothing is found, it will extract the given sequence's elements in such a way that all elements are present only once, and ordered from the last found to the first one.
+The program will then try all combinations with a adding length limit of the initial sequence's length.
+This part has a $n!$ complexity, but it is rarely reached because it is easy to find a solution.
+
+Given a sequence on which we would like to search, we try to compress it using several \textcolor{green}{amb}:
+
+At first, we try an operator, $C$ and then $I$.
+
+Given an operator, we decide a searching size.
+We will try from 1 up to the sequence's length.
+A size represents what is taken from a list in order to search on it.
+This parameter is important, for example to detect incrementation from an operator to another, like in the next section example.
+
+Once an operator and a size has been chosen, we compress the sequence from the left to the right by going as far as possible and appending result to previous results until the rest is empty
+(if the rest is not long enough to be taken \textit{size} elements, the program will \textcolor{red}{fail}).
+
+Once a list has been compressed, it is rejected if all found operators are only applied once.
+
+Its complexity is then compared to the initial sequence's one, and the best one is kept (if complexities are equal, the previous sequence is kept and we \textcolor{red}{fail}).
+
+If we were able to compress until we have got only an operator and its arguments (3 for $C$ and 4 for $I$), we check if arguments are coherent and if so, finally extend it, by increasing its times and then uncompress the final sequence.
+
+I also implemented a way to look after ALL solutions, but as the adding part has a $n!$ complexity, this way takes a very long time to return.
+
+For any implementation considering, see the program documentation as explained in my git repository README.
+I spent quite a long time writing it as exhaustive as possible, so that a good comprehension of the program is possible.
 
@@
 
-As we saw before, when we find an increment operator used only once (\textit{times} = 1), its \textit{where} field doesn't mean anything, as when decompressed, \textit{argument} is only extracted, $I$, \textit{times} and \textit{where} fields being simply removed from the sequence.
+As we saw before, when we find an increment operator used only once (\textit{times} = 1), its \textit{where} field doesn't mean anything, as when it is decompressed, \textit{argument} is only extracted, $I$, \textit{times} and \textit{where} fields being simply removed from the sequence.
 
-Normally, such a representation should be rejected because it is trivially less compressed than just writing \textit{argument} as is.
-It may be useful this example :
+Normally, such a representation should be rejected because trivially, it is less compressed than just writing \textit{argument} as is.
+It may be useful in this example :
 $$1\ 1\ 1\ 2\ 1\ 1\ 2\ 1\ 2\ 3\ 1\ 1\ 2\ 1\ 2\ 3\ 1\ 2\ 3\ 4$$
-Let compress it using our method (sequence is cut for better understanding):
+Let us compress it using our method (sequence has been cut for better understanding):
 $$1\ 0\ 1\ I$$
@@
 This is of course one over a lot of obtainable solutions, but it is findable by our process so we have the right to consider it.
-Here we will make an 'error' which will cost us the solution:
+Here we will make an "error" which will cost us the solution:
 $$\{\ 1\ 0\ 1\ I\ \}\ \textcolor{red}{0}\ 1\ I$$
@@
 
-A solution would be to use a 'joker', like Factor's $f$ in order to warn when compared with an other value that this value has not been defined yet.
+A solution would be to use a "joker", like Factor's $f$ in order to warn, when compared with an other value, that this value has not been defined yet.
 For now, the program is not able to solve this problem without removing the first lonely $1$.
@@
 
-An other way to improve the program is to solve the 'how to indicate where to apply the increment-operator in a natural, compressed and Kantian way' problem.
+An other way to improve the program would be to solve the "how to indicate where to apply the increment-operator in a natural, compressed and Kantian way" problem.
 
-It has been there since the beginning of the project, and even if a lots of plus or minus elegant solutions have been found, a lot of work is to been done on this subject.
+It has been there since the beginning of the project, and even if a lots of plus or minus elegant solutions have been found, a lot of work has to been done on this subject.
 
@@
 As explained before, the use of short memory is not reliable and quite difficult to implement.
-Even though a whole implementation has been done, it is not used in final version because of its random behaviour.
+Even though a whole implementation has been done, it has not used in final version because of its random behaviour.
 
@@
 
-This project has been an excellent way to use at a project scale a new and powerful language as Factor.
+This project has been an excellent way to use, at a project scale, a new and powerful language as Factor.
 

### 2011-07-02 article.tex
Started huge corrections

@@
 
-\title{Sequences complexity}
+\title{Sequence complexity}
 \author{Axel Schumacher\\Télécom ParisTech\\Free Project}
@@
 
-As a student at Télécom ParisTech, I chose to follow the 'Non-classic languages paradigms' course with Samuel Tardieu\cite{samuel}, while working on a free project with Jean-Louis Dessalles\cite{jld}.
-Jean-Louis Dessalles suggested a project based on a Komolgorov's complexity problem: given a small sequence of digits, shapes or characters, I had to design a small program able to complete this list as well as an eight-years old children.
+As a student at Télécom ParisTech, I chose to follow the 'Non-classical language paradigms' course with Samuel Tardieu\cite{samuel}, while working on a free project with Jean-Louis Dessalles\cite{jld}.
+Jean-Louis Dessalles suggested a project based on a Komolgorov complexity problem: given a small sequence of digits, shapes or characters, I had to design a small program able to complete this list as well as an eight-year old child.
 \cite{starting_point}
 
-The main goal of this project is to apply Kolmogorov theory on the given list in order to compress it in a optimal and human way, so that we will then be able to extend that list using found compression process.
-On the 'Non-classic languages paradigms' course, we learned small spread languages as Haskel, Scala or Factor, and we were also supposed to perform a small implementation project using one of those languages.
+The main goal of this project is to apply Kolmogorov theory to the given list in order to compress it in an optimal and human way.
+This would then able us to extend that list using that compression.
+During the "Non-classic language paradigms" course, we studied small spread languages as Haskel, Scala or Factor, and we were also supposed to perform a small implementation project using one of those languages.
 
@@
 
-\section{Problematic}
+\section{Problem description}
 

### 2011-07-03 article.tex
Started HUGE corrections

@@
 \usepackage{color}
-
+%  {\color{blue} minimal}
+%apply to
 \begin{document}
@@
 
-As a student at Télécom ParisTech, I chose to follow the 'Non-classical language paradigms' course with Samuel Tardieu\cite{samuel}, while working on a free project with Jean-Louis Dessalles\cite{jld}.
-Jean-Louis Dessalles suggested a project based on a Komolgorov complexity problem: given a small sequence of digits, shapes or characters, I had to design a small program able to complete this list as well as an eight-year old child.
-\cite{starting_point}
+As a student at Télécom ParisTech, I chose to follow the 'Non-classic language paradigms' course with Samuel Tardieu\cite{samuel}, 
+while working on a free project with Jean-Louis Dessalles\cite{jld}.
+Jean-Louis Dessalles suggested a project based on a Komolgorov complexity problem:
+given a small sequence of digits, shapes or characters, I had to design a small program able to complete this 
+list as well as an eight-year-old child. \cite{starting_point}
 
-The main goal of this project is to apply Kolmogorov theory to the given list in order to compress it in an optimal and human way.
-This would then able us to extend that list using that compression.
-During the "Non-classic language paradigms" course, we studied small spread languages as Haskel, Scala or Factor, and we were also supposed to perform a small implementation project using one of those languages.
+The main goal of this project was to apply Kolmogorov theory to the given list in order to compress it in an
+optimal and human way. This will then enable us to extend that list using the compression.
+During the 'Non-classic language paradigms course, we studied uncommon languages such
+as Haskel, Scala or Factor; we also were to 
+perform a small implementation project using one of those languages.
 
-Factor\cite{factor} is a quite memory-close language, able to perform backtracking as well as Prolog using continuations and working on a stack, like a logical sequence.
+Factor\cite{factor} is a quite memory-close language, able to perform backtracking as well as Prolog using continuations and working on a stack.
 Its powerful and non-standard architecture makes it a very interesting language to work on, and this is why I chose to use it to implement my project.
@@
 
-Humans capabilities to compress and understand structures have always fascinated computer sciences researchers.
-Humans are able to perform perfectly tasks as recognizing a person's face, understand a language or, in our scope of interest, understand and complete a list of digits, alphabetics or shapes.
-Those tasks are very difficult to be completed efficiently by machines, even using the most powerful computers.
-That is why a huge domain of research still exists on that subject, always with the same goal: give machines more and more of our "human intelligence".
+Human capabilities to compress and understand structures have always fascinated computer science researchers.
+Humans are able to perfectly perform tasks such as recognizing a person's face, understanding
+a language or, in our scope of interest, understanding and completing a list of digits, alphabetics or shapes.
+Those tasks are very difficult for machines, even using the most powerful computers.
+That is why much research is left to be done on the subject, always with the same goal: give machines more and more of our "human intelligence".
 
@@
 
-We are now to try to light up some darks areas of this problem.
+We will first illustrate the problem with an example.
 Let us imagine a very simple sequence:
 $$1\ 2\ 2\ 3\ 3\ 3$$
-Any eight-years old children would easily suggests that a good continuation of this sequence would be:
+Any eight-year old child would easily suggest
+that a good continuation of this sequence would be:
 $$1\ 2\ 2\ 3\ 3\ 3\ 4\ 4\ 4\ 4$$
 But how can one be so sure about it?
-This is where we can introduce the notion of "complexity", and more especially Kolmogorov's one:
+This is where we can introduce the notion of "complexity", and more especially Kolmogorov complexity:
 
-"In algorithmic information theory (a subfield of computer science), the Kolmogorov complexity of an object, such as a piece of text, is a measure of the computational resources needed to specify the object." \cite{wikipedia_kolmogorov}
+"In algorithmic information theory (a subfield of computer science), the Kolmogorov complexity of an object,
+such as a piece of text, is a measure of the computational resources needed to specify the object." \cite{wikipedia_kolmogorov}
 
-In other words, this complexity has the particularity to highly depends of the user, and is moreover really difficult to use it inside a program.
+In other words, this complexity has the particularity 
+that it highly depends on the user, and is moreover really difficult to use inside a program.
 
-Using this complexity, someone could define $1\ 2\ 2\ 3\ 3\ 3$ as "count from one and repeat each number as much as itself", which is really easier to understand, memorize and extend for an human than a random sequence, like a telephone or credit card number.
+Using this complexity, someone could define $1\ 2\ 2\ 3\ 3\ 3$ as "count from one and repeat each number as much as itself",
+which is really easier to understand, memorize and extend for an human than a random sequence, like a telephone or credit card number.
 We will explore different ways to represent and manipulate such informations.
 
-An other way to compute a list's complexity would be to use \textit{short term memory}, a list or tree containing last used elements.
-An access to one of those elements would be its binary coded address, for example.
-This model is easily explainable considering that a human, if he was able to solve a problem using a specific operator, will naturally try this operator first when confronted to a new problem.
-This list is implemented but not used because of its unpredictable character.
+Another way to compute the complexity of a list would be to use
+\textit{short term memory}, a list or tree containing the elements used last.
+An access to one of those elements would be its binary encoded address, for example.
+This model is easily explainable considering that a human, if he was able to solve a problem using a specific operator,
+would naturally try this operator first when confronted with a new problem.
+This list is implemented but not used because of its unpredictable nature.
 
-That is why in the present version a standard \textit{binary coding} is used to compute a list's complexity, with 0 costing 0.
+That is why in the present version a standard \textit{binary encoding} is used to compute the complexity of a list , with 0 costing 0.
 
-Given a way to compute complexity, one can try to compress a list using \textit{operators} while resulting complexity is lower than initial sequence's one.
+Given a way to compute complexity, one can try to compress a list using \textit{operators} while the
+resulting complexity is lower than that of the initial sequence.
 
@@
 
-At first, I thought about using Factor's \textit{tuples}, special sequences of easily sharable between descendants fields, like standard \textit{Object Oriented Programming}.
+At first, I thought about using Factor's \textit{tuples}, special fields sequences which are easily sharable between descendants, as in standard \textit{Object Oriented Programming}.
 
@@
 \begin{itemize}
-  \item{cost, a function returning an operator's cost regarding its fields values.}
-  \item{apply, a function which uses a sequence and generate a sequence by uncompressing this operator on it (often using only its first element).}
-  \item{search, a function which tries to find current operator's application on a sequence.}
+  \item{\textit{cost}, a function returning an operator's cost which adds the values of its fields.
+  \item{\textit{apply}, a function which uses a sequence and generates another sequence by uncompressing this operator on it (often using only its first element).}
+  \item{\textit{search}, a function which tries to find the current operator's application on a sequence.}
 \end{itemize}
@@
 \begin{itemize}
-  \item{A copy operator: using its predecessor's \textit{times} field, copies given argument \textit{times} times. }
+  \item{A copy operator: using its predecessor's \textit{times} field, copies a \textit{times} number of times the given argument.}
   \item{
-    An increment operator: increments and copy given argument \textit{times} times.
-    If this argument is an operator, it will copy it by incrementing its \textit{times} field. }
-  \item{A step operator: also contains a \textit{gap} argument and an \textit{operator} field, applies its operator by skipping as much elements as given by \textit{gap} on a list.}
+    An increment operator: increments and copies a \textit{times} number of times the given argument.
+    If this argument is an operator, it will copy it by incrementing its \textit{times} field.}
+  \item{A step operator: also contains a \textit{gap} argument and an \textit{operator} field, applies its operator by skipping as many
+elements as given by \textit{gap} on a list.}
 \end{itemize}
 
-The step operator was useful for this case:
+The step operator was useful in this case: 
 $$1\  2\  2\  3\  3\  3\  4\  4\  4\  4$$
@@
 Using step operator, it gives:
-$$(step\ operator\ times(4)\ gap(1)\ operator(increment\ times(1)))\ 1\ 2\ 3\ 4$$
-The step operator will apply three times with a gap of one.
+$$(step\ operator\ times(4)\ gap(1)\ operator(increment\ times(1)))\ (copy\ times(1))\ 1\ 2\ 3\ 4$$
+The step operator will be applied four times with a gap of one.
 As between each gap we only have one element, the increment operator in \textit{operator} field only applies once each time.
-The step operator will apply on the directly following element, the copy operator.
+The step operator will be applied to the directly following element, the copy operator.
 A final compression would give:
-$$(step\ operator\ times(4)\ gap(1)\ operator(increment\ times(1)))$$
+$$(step\ operator\ times(4)\ gap(1)\ operator(increment\ times(1))) (copy\ times(1))$$
 $$(increment\ times(4))\ 1$$
 
-Speaking of complexity, if we count 1 for each operator plus recursive cost of all its arguments, the sequence $1\ 2\ 2\ 3\ 3\ 3\ 4\ 4\ 4\ 4$ will cost 23, where the compressed version costs 14.
+In terms of complexity, if we count 1 for each operator plus the recursive cost of all its arguments,
+the raw sequence $1\ 2\ 2\ 3\ 3\ 3\ 4\ 4\ 4\ 4$ will cost 23, while the compressed version costs 14.
 Hence, we can say that we have a compressed version.
 
-Copy and increment search were easy, I just had to compare current result with the next sequence's element.
-But for the step-operator, how to determine the gap before searching?
+Copy and increment search were easy, I just had to compare the current result with the next sequence's element.
+However, for the step-operator, how could I determine the gap before searching?
 I tried each operator but with a gap of one.
-The problem was that it didn't used all the power of the step operator, but the search would cost a lot in another way.
-And what does a step operator applied on a step operator would mean?
-A real complex, not useful nor handy object actually.
+The problem was that it didn't use all the power of the step operator, but the search would cost a lot otherwise.
+And what would a step operator applied on a step operator mean?
+A very complex, not useful nor handy object actually.
 
-An other problem is that it is difficult to extend a list, what specific operator should we "times-increment"?
+Another problem is that it is difficult to extend a list:
+what specific operator should we "times-increment"?
 On this particular example, it is the first operator of the list, but can we be sure about it?
-And foremost, how can we be sure about the fact that a list \textit{is} extendible?
+Moreover, how can we be sure about the fact that a list \textit{is} extensible?
 
-This solution displeased Jean-Louis Dessalles, because of this not really "natural" strange step-operator, and its difficulties to be understood and used.
-That is why he asked me to only use two operators: copy and increment.
-His point was that in the previous example, increment operator should have been applied at the same time on copy operator and on digits.
-Therefore, I should put the argument into the operator instead of leaving it on the list.
+This solution displeased Jean-Louis Dessalles, because of this not really "natural" strange step-operator, and the difficulty 
+for it to be understood and used.
+That is why he asked me to use only two operators: copy and increment.
+His point was that in the previous example, the 
+increment operator should have been applied at the same time on copy operator and on digits.
+Therefore, I should put the argument into the operator instead of leaving it in the list.
 Then, the increment operator would have seen a sequence of copy operator incrementing at the same time their \textit{times} and \textit{argument} fields.
 
-\subsection{Two operators with inelegant application}
+\subsection{Two operators with an inelegant application}
 
-Now with this constraining consign, the question was: "How can I apply different operators on the same object but on different fields?"
-I imagined a solution that I found pretty ugly, but functional: copy-operator would now both know its \textit{argument} and \textit{times}.
-Increment-operator would inherit from copy-operator and moreover know where in his \textit{argument} it would apply: on its \textit{argument}, its \textit{times} or both.
-This information was stored on a \textit{where} field.
+Now with this constraining instruction, the question was: "How can I apply different operators on the same object but on different fields?"
+I imagined a solution that I found ugly, but functional.
+Copy-operator would now know both its \textit{argument} and its \textit{times}.
+Increment-operator would inherit from copy-operator and moreover know where in its \textit{argument} it would apply:
+on its \textit{argument}, its \textit{times} or both.
+This information was stored in a \textit{where} field.
 
-Here is an application on previous example (first parenthesis contain \textit{argument}, second \textit{times} and last \textit{where}):
+Here is an application on the previous example
+(the first set of parenthesis contains \textit{argument}, the second set contains \textit{times} and the last set contains \textit{where}):
 $$1\ 2\ 2\ 3\ 3\ 3\ 4\ 4\ 4\ 4$$
-$$(increment(1)(1)(arg))\ (increment(2)(2)(arg))\ (increment(3)(3)(arg))$$
-$$(increment(increment(1)(1)(arg))(3)(both))$$
+$$(copy(1)(1))\ (copy(2)(2))\ (copy(3)(3))\ (copy(4)(4))$$
+$$(increment(copy(1)(1))(4)(both))$$
 
-The \textit{where} field doesn't have any meaning when applying on a digit, and this is already a structural problem.
-This same field also doesn't have any meaning when applying on an increment-operator: it cannot apply on its argument because it is the contained increment-operator which takes care of that, and hence can only apply on its \textit{times}.
+The \textit{where} field doesn't have any meaning when applied to
+a digit, and this is already a structural problem.
+This same field also doesn't have any meaning when applied to an increment-operator: it cannot apply to its \textit{argument} because the contained increment-operator takes care of that,
+and hence can only apply on its \textit{times}.
 
-With this solution, part of previous problems were solved: a list is only extendible if it can be reduced to one operator, and to extend it we only have to increment its \textit{times} field and then recursively decompress it.
-Furthermore, putting any operator in the \textit{operator} field of an increment-operator will always have a meaning, like we can imagine in this situation:
+With this solution, some of the previous problems were solved:
+a list is only extensible if it can be reduced to one operator,
+and to extend it we only have to increment its \textit{times} field and then recursively decompress it.
+Furthermore, putting any operator in the \textit{argument} field of an increment-operator will always have a meaning,
+as we can imagine in the following situation:
 $$1\ 1\ 1\ 2\ 1\ 1\ 2\ 1\ 2\ 3\ 1\ 1\ 2\ 1\ 2\ 3\ 1\ 2\ 3\ 4$$
@@
 
-During a meeting with both Samuel Tardieu and Jean-Louis Dessalles, this solution worked pretty well, putting apart some complexity problems: sometimes "good" (think "expected") solutions were not kept because they costed more than uncompressed sequence.
+During a meeting with both Samuel Tardieu and Jean-Louis Dessalles, this solution worked pretty well, {\color{blue}{apart from 
+}}
+some complexity problems: sometimes "good" (think "expected") solutions were not kept because they {\color{blue}{cost
+}}
+ more than {\color{blue}{the
+}} 
+uncompressed sequence.
 For example, with $1\ 2\ 2\ 3\ 3\ 4$, the program considered three increments of two times in a row, but rejected it.
-For the "dirty" where-to-apply solution, Samuel cleverly suggested that instead of a restrictive three-choices field, I should use a indexes list which could also handle deepness, indicating where the increment-operator should apply.
+For the "dirty" where-to-apply solution, Samuel cleverly suggested that instead of a restrictive {\color{blue}{
+three-choice }}field, I should use {\color{blue}{an indexed
+}} list which could also handle deepness, indicating where the increment-operator should apply.
 This is the solution I adopted and customized in my final version.
@@
 
-Current solution is axed on Factor's suffixed way: an operator is represented by a letter, $C$ for copy or $I$ for increment, and applies on a specified number of arguments BEFORE it.
-Elements in a compressed sequence are only compressed sequences, digits or operators letters.
+Current solution is axed on Factor's suffixed way: an operator is represented by a letter, $C$ for copy or $I$ for increment, and applies {\color{blue}{to
+}}
+ a specified number of arguments BEFORE it.
+Elements in a compressed sequence are only compressed sequences, digits or {\color{blue}{operator
+}}
+ letters.
 Customized indexes work that way: increment operators own in their \textit{where} field a sequence of digits, which are indexes representing an element's absolute position in extended \textit{argument}.
@@
 
-Jean-Louis Dessalles wasn't really satisfied by this index solution: it wouldn't respect Kantian structural form of the model
+Jean-Louis Dessalles wasn't really satisfied by this index solution: it wouldn't respect {\color{blue}{the
+}}
+ Kantian structural form of the model
 (we should be able to manipulate shapes or vegetables as well and using them all along the model) and the structure is absolutely not represented using it.
-He suggested the use of masks, more "natural" and compressed than my indexes notation, but it doesn't solve the structure's respect problem and it is actually in bijection with my system
-(as it is more important to act simply and 'humanly' than saving RAM, we can neglect the compression difference).
+He suggested the use of masks, more "natural" and compressed than my {\color{blue}{indexed
+}}
+ notation, but it doesn't solve the structure's respect problem and it is actually in bijection with my system
+(as it is more important to act simply and 'humanly' than {\color{blue}{to save 
+}} RAM, we can neglect the compression difference).
 
-For easier representation, an \textit{argument} or a \textit{where} field reduced to only one element is not contained into a sequence, but inserted as is.
+For easier representation, an \textit{argument} or a \textit{where} field reduced to only one element is not contained {\color{blue}{in
+}} a sequence, but inserted as is.
 
-For results purpose, $C$ and $I$ words don't cost anything.
+For {\color{blue}{result
+}}
+ purpose, $C$ and $I$ words don't cost anything.
 
@@
 
-Let us see closer how does search algorithm work, using Factor's backtracking power.
+Let us {\color{blue}{now take a closer look at at how the search algorithm works
+}}, using Factor's backtracking power.
 
@@
 If there is no element left, this level is abandoned and the previous one is considered.
-This system, quite close to Prolog's one, is useful to try possibilities at different levels, and backtrack in case of failure to the next possibility.
+This system, quite close to {\color{blue}{Prolog's
+}}, is useful {\color{blue}{for trying
+}}
+ possibilities at different levels, and {\color{blue}{backtracks to the next possibility in case of failure.
+}}
 
@@
 We will try from 1 up to the sequence's length.
-A size represents what is taken from a list in order to search on it.
-This parameter is important, for example to detect incrementation from an operator to another, like in the next section example.
+A size represents what is taken from a list in order to search {\color{blue}{it
+}}.
+This parameter is important, for example to detect incrementation from an operator to another, {\color{blue}{as in the example shown in the next section .
+}}
 
-Once an operator and a size has been chosen, we compress the sequence from the left to the right by going as far as possible and appending result to previous results until the rest is empty
+Once an operator and a size {\color{blue}{have
+}} been chosen, we compress the sequence from the left to the right by going as far as possible and appending result to previous results until the rest is empty
 (if the rest is not long enough to be taken \textit{size} elements, the program will \textcolor{red}{fail}).
@@
 
-This is of course one over a lot of obtainable solutions, but it is findable by our process so we have the right to consider it.
+This is of course one {\color{blue}{of many
+}} obtainable solutions, but it is findable by our process so we have the right to consider it.
 Here we will make an "error" which will cost us the solution:
@@
 
-It has been there since the beginning of the project, and even if a lots of plus or minus elegant solutions have been found, a lot of work has to been done on this subject.
+It has been there since the beginning of the project, and even if{\color{blue}{many more or less 
+}} elegant solutions have been found, a lot of work {\color{blue}{remains
+}} to been done on this subject.
 
@@
 
-This project has been an excellent way to use, at a project scale, a new and powerful language as Factor.
+This project has been an excellent way to use, at a project scale, a new and powerful language {\color{blue}{such 
+}}as Factor.
 
-It revealed itself difficult to use at first but incredibly efficient for this particular subject.
+It {\color{blue}{turned out to be 
+}}difficult to use at first but incredibly efficient for this particular subject.
 The project itself proved to be harder than expected, because of its 'human' restriction.
@@
 
-This was an enriching experience and it worthed spending time working on it.
+This was an enriching experience and {\color{blue}{well worth the time spent 
+}}working on it.
 

### 2011-07-03 article.tex
Correction done, one last reading left

@@
 \usepackage{color}
-%  {\color{blue} minimal}
-%apply to
+
 \begin{document}
@@
 \newpage
+
+\section*{Acknowledgements}
+
+My warm thanks to Jon Harper, who helped me a lot through the difficult process of learning Factor, and also to my two professors,
+Samuel Tardieu and Jean-Louis Dessalles, my supervisors, who spent time discussing my project and helping me.
 
@@
 \begin{itemize}
-  \item{\textit{cost}, a function returning an operator's cost which adds the values of its fields.
+  \item{\textit{cost}, a function returning an operator's cost which adds the values of its fields.}
   \item{\textit{apply}, a function which uses a sequence and generates another sequence by uncompressing this operator on it (often using only its first element).}
@@
 Furthermore, putting any operator in the \textit{argument} field of an increment-operator will always have a meaning,
-as we can imagine in the following situation:
+as we can imagine in the following more complicated situation:
 $$1\ 1\ 1\ 2\ 1\ 1\ 2\ 1\ 2\ 3\ 1\ 1\ 2\ 1\ 2\ 3\ 1\ 2\ 3\ 4$$
-Compression would give (sequence has been cut for better understanding):
+which can be segmented in the following fashion:
+$$1*\ 1;\ 1\ 2*\ 1;\ 1\ 2;\ 1\ 2\ 3*\ 1;\ 1\ 2;\ 1\ 2\ 3;\ 1\ 2\ 3\ 4$$
+Compression would give (the sequence has been cut for the sake of clarity):
 $$(increment(1)(1)(arg))$$
@@
 
-An other time would give:
-$$(increment(increment(1)(1)(arg))(1)(times))$$
+Another time would give:
+$$(increment(increment(1)(1)(arg))(1)(\textcolor{red}{times}))$$
 $$(increment(increment(1)(1)(arg))(2)(times))$$
@@
 
-This solution is findable, putting apart the complexity problem (see below), and a huge problem which is at second iteration, how did it know that increment applied once applied only on \textit{times} and not something else?
-I chose \textit{times} because it has been able to compress a last time, given that all increment operators applied on \textit{times}, but I had no right to do so.
+This solution is findable, apart from the complexity problem (see below), and the following problem: at the second iteration, how did it know that increment, when applied once, applied only to \textit{times} and not to something else?
+I chose \textit{times} because it has been able to compress at the last iteration, given that all the increment operators applied to \textit{times}, but I had no right to do so.
 
-During a meeting with both Samuel Tardieu and Jean-Louis Dessalles, this solution worked pretty well, {\color{blue}{apart from 
-}}
-some complexity problems: sometimes "good" (think "expected") solutions were not kept because they {\color{blue}{cost
-}}
- more than {\color{blue}{the
-}} 
-uncompressed sequence.
-For example, with $1\ 2\ 2\ 3\ 3\ 4$, the program considered three increments of two times in a row, but rejected it.
-For the "dirty" where-to-apply solution, Samuel cleverly suggested that instead of a restrictive {\color{blue}{
-three-choice }}field, I should use {\color{blue}{an indexed
-}} list which could also handle deepness, indicating where the increment-operator should apply.
+During a meeting with both Samuel Tardieu and Jean-Louis Dessalles, this solution worked well enough, apart from 
+some complexity problems: sometimes "good" (think "expected") solutions were not kept because they cost
+more than the uncompressed sequence.
+For example, Samuel Tardieu suggested $1\ 2\ 2\ 3\ 3\ 4$, with segmentation $1\ 2\ *\ 2\ 3\ *\ 3\ 4$ in mind,
+the program considered three increments in a row, each applied twice, but rejected it.
+For the "dirty" where-to-apply solution, Samuel Tardieu suggested that instead of a restrictive
+three-choice field, I should use an indexed list which could also handle deepness, indicating where the increment-operator should apply.
 This is the solution I adopted and customized in my final version.
@@
 
-Current solution is axed on Factor's suffixed way: an operator is represented by a letter, $C$ for copy or $I$ for increment, and applies {\color{blue}{to
-}}
+The current solution is based on Factor's suffix paradigm: an operator is represented by a letter, $C$ for copy or $I$ for increment, and applies to
 a specified number of arguments BEFORE it.
-Elements in a compressed sequence are only compressed sequences, digits or {\color{blue}{operator
-}}
- letters.
-Customized indexes work that way: increment operators own in their \textit{where} field a sequence of digits, which are indexes representing an element's absolute position in extended \textit{argument}.
+Elements in a compressed sequence are only compressed sequences, digits or operator letters.
+My customized indexes work that way: increment operators own in their \textit{where} field a sequence of digits,
+which are indexes representing an element's absolute position in the extended \textit{argument}.
 For example, let us consider the following sequence:
 $$\{\ a_0\ a_1\ \{\ a_2\ \{\ a_3\ a_4\ \}\ a_5\ \{\ a_6\ \}\ \}\ a_7\ \{\ a_8\ \}\ a_9\ \}$$
-Indexes are extended indexes.
-Hence, any deepness level can be reached, and there is no need to recall structural information, like with tree indexes, in which case element $a_4$ would be accessed with $2.1.1$ instead of $4$.
-This notation is easier to manipulate and resulting \textit{where} sequence may even be compressed!
+When extended, this sequence would be:
+$$\{\ a_0\ a_1\ a_2\ a_3\ a_4\ a_5\ a_6\ a_7\ a_8\ a_9\ \}$$
+I use the extended indexes.
+Hence, any deepness level can be reached, and there is no need to recall structural information,
+as with tree indexes, in which case element $a_4$ would be accessed with $2.1.1$ instead of simply $4$.
+This notation is easier to manipulate and the resulting \textit{where} sequence could even be compressed!
 
-Jean-Louis Dessalles wasn't really satisfied by this index solution: it wouldn't respect {\color{blue}{the
-}}
- Kantian structural form of the model
-(we should be able to manipulate shapes or vegetables as well and using them all along the model) and the structure is absolutely not represented using it.
-He suggested the use of masks, more "natural" and compressed than my {\color{blue}{indexed
-}}
- notation, but it doesn't solve the structure's respect problem and it is actually in bijection with my system
-(as it is more important to act simply and 'humanly' than {\color{blue}{to save 
-}} RAM, we can neglect the compression difference).
+Jean-Louis Dessalles wasn't really satisfied with this index solution:
+it wouldn't respect the Kantian structural form of the model
+(we should be able to manipulate shapes or vegetables as well, and use only them in the model).
+Moreover, the structure is absolutely not represented.
+He suggested the use of masks, more "natural" and compressed than my index notation,
+but this doesn't solve the Kantian problem and it is actually in bijection with my system
+(as it is more important to act simply and 'humanly' than to save RAM, we can neglect the compression difference).
 
-For easier representation, an \textit{argument} or a \textit{where} field reduced to only one element is not contained {\color{blue}{in
-}} a sequence, but inserted as is.
+For easier representation, an \textit{argument} or a \textit{where} field reduced to only one element is not contained in a sequence, but inserted as is.
 
-For {\color{blue}{result
-}}
- purpose, $C$ and $I$ words don't cost anything.
+For result purposes, $C$ and $I$ words won't cost anything.
 
-We also define operators' arguments order:
+We also define the order of the arguments of the operators:
 \begin{itemize}
@@
 $$\{\ 1\ 1\ C\ \}\ \{\ 0\ 1\ \}\ 4\ I$$
-We only have one operator left, just with its arguments.
+We only have one operator left, $I$, with just its arguments.
 We increment its \textit{times} field:
 $$\{\ 1\ 1\ C\ \}\ \{\ 0\ 1\ \}\ 5\ I$$
-And decompress it to obtain logical extension:
+And decompress it to obtain its logical extension:
 $$1\ 1\ C\ 2\ 2\ C\ 3\ 3\ C\ 4\ 4\ C\ 5\ 5\ C$$
@@
 
-Let us {\color{blue}{now take a closer look at at how the search algorithm works
-}}, using Factor's backtracking power.
+Let us now take a closer look at how the search algorithm works, using Factor's backtracking power.
 
-\subsection{\textcolor{green}{amb} and \textcolor{red}{fail}}
+\subsection{\textcolor{blue}{amb} and \textcolor{red}{fail}}
 
-Using continuations in factor, we can use \textcolor{green}{amb} to test all elements in a sequence.
-When \textcolor{red}{fail} is called, the program comes back to the last \textcolor{green}{amb} call and tries its next element.
+Using continuations in factor, we can use the existing function \textcolor{blue}{amb} to test all the elements of a sequence.
+When \textcolor{red}{fail} is called, the program backtracks to the last \textcolor{blue}{amb} call and tries its next element.
 If there is no element left, this level is abandoned and the previous one is considered.
-This system, quite close to {\color{blue}{Prolog's
-}}, is useful {\color{blue}{for trying
-}}
- possibilities at different levels, and {\color{blue}{backtracks to the next possibility in case of failure.
-}}
+This system, quite close to Prolog's, is useful for trying
+possibilities at different levels, and backtracks to the next possibility in case of failure.
 
@@
 
-As it is able to complete incomplete sequences, the program will first try to remove from 0 to the length minus 2 elements.
+My program is able to complete incomplete sequences: it will first try to remove a number of elements from 0 to the sequence length minus 2.
 At each removal, it will check if when extended the resulting sequence contains the initial one and \textcolor{red}{fail} otherwise.
 
-If nothing is found, it will extract the given sequence's elements in such a way that all elements are present only once, and ordered from the last found to the first one.
-The program will then try all combinations with a adding length limit of the initial sequence's length.
-This part has a $n!$ complexity, but it is rarely reached because it is easy to find a solution.
+If nothing is found, the program will extract the elements of the given sequence in such a way that all elements are present only once, and ordered from the last found to the first one.
+The program will then try to add all combinations, it starts with adding one element, then two, and so on until the length of the initial sequence is reached.
+This part has a theoretically factorial complexity, but in practice this is almost never reached because a solution is quickly found.
 
-Given a sequence on which we would like to search, we try to compress it using several \textcolor{green}{amb}:
+Given a sequence which we would like to search on, we try to compress:
 
@@
 Given an operator, we decide a searching size.
-We will try from 1 up to the sequence's length.
-A size represents what is taken from a list in order to search {\color{blue}{it
-}}.
-This parameter is important, for example to detect incrementation from an operator to another, {\color{blue}{as in the example shown in the next section .
-}}
+We will try from 1 up to the length of the sequence.
+A size represents what is taken from a list in order to search it.
+This parameter is important, for example to detect incrementation from an operator to another, as in the example shown in the previous section.
 
-Once an operator and a size {\color{blue}{have
-}} been chosen, we compress the sequence from the left to the right by going as far as possible and appending result to previous results until the rest is empty
-(if the rest is not long enough to be taken \textit{size} elements, the program will \textcolor{red}{fail}).
+Once an operator and a size have been chosen, we compress the sequence from the left to the right by going as far as possible and appending the result to the previous results until the rest is empty
+(if the rest is not long enough to be shortened by \textit{size} elements, the program will \textcolor{red}{fail}).
 
-Once a list has been compressed, it is rejected if all found operators are only applied once.
+Once a list has been compressed, it is rejected if all the operators which have been found are only applied once.
 
-Its complexity is then compared to the initial sequence's one, and the best one is kept (if complexities are equal, the previous sequence is kept and we \textcolor{red}{fail}).
+Its complexity is then compared to that of the initial sequence, and the best one is kept (if complexities are equal, we \textcolor{red}{fail}).
 
-If we were able to compress until we have got only an operator and its arguments (3 for $C$ and 4 for $I$), we check if arguments are coherent and if so, finally extend it, by increasing its times and then uncompress the final sequence.
+If we were able to compress until only one operator and its arguments (2 for $C$ and 3 for $I$) are left,
+we check that the arguments are coherent and if so, we finally extend it: we increase its \textit{times} and then decompress the final sequence.
 
-I also implemented a way to look after ALL solutions, but as the adding part has a $n!$ complexity, this way takes a very long time to return.
+I also implemented a way to look at ALL the solutions, but as the adding part has a factorial complexity, this takes a very long time to terminate.
 
-For any implementation considering, see the program documentation as explained in my git repository README.
-I spent quite a long time writing it as exhaustive as possible, so that a good comprehension of the program is possible.
+For questions on implementation, see the program documentation as explained in my git repository README.\cite{git}
+I spent quite a long time writing it as exhaustively as possible, in order to insure a good comprehension of the program.
 
-\section{Ways to continue}
+\section{Perspectives}
 
-\subsection{Once applied increment operators}
+\subsection{Increment operators which are applied only once}
 
-As we saw before, when we find an increment operator used only once (\textit{times} = 1), its \textit{where} field doesn't mean anything, as when it is decompressed, \textit{argument} is only extracted, $I$, \textit{times} and \textit{where} fields being simply removed from the sequence.
+As we saw before, when we find an increment operator which is used only once (\textit{times} = 1),
+its \textit{where} field doesn't mean anything, as when it is decompressed, only \textit{argument} is extracted,
+whereas the $I$, \textit{times} and \textit{where} fields are simply removed from the sequence.
 
 Normally, such a representation should be rejected because trivially, it is less compressed than just writing \textit{argument} as is.
-It may be useful in this example :
+It may be useful in this example:
 $$1\ 1\ 1\ 2\ 1\ 1\ 2\ 1\ 2\ 3\ 1\ 1\ 2\ 1\ 2\ 3\ 1\ 2\ 3\ 4$$
-Let us compress it using our method (sequence has been cut for better understanding):
+Let us compress this sequence using our method (again the sequence has been cut for the sake of clarity):
 $$1\ 0\ 1\ I$$
@@
 
-This is of course one {\color{blue}{of many
-}} obtainable solutions, but it is findable by our process so we have the right to consider it.
+This is of course one of many obtainable solutions, but it is findable by our process so we have the right to consider it.
 Here we will make an "error" which will cost us the solution:
@@
 $$\{\ 1\ 0\ 1\ I\ \}\ \textcolor{green}{2}\ 4\ I$$
-Now, we would like to obtain
-$$\{\ \{\ 1\ 0\ 1\ I\ \}\ 2\ 1\ I\ \}\ 6\ 4\ I$$
-but our program will \textcolor{red}{fail} when comparing $0$ and $2$.
+Now, we would like to obtain:
+$$\{\ \{\ 1\ 0\ 1\ I\ \}\ 2\ 1\ I\ \}\ 5\ 4\ I$$
+but our program will \textcolor{red}{fail} when comparing $0$ with $2$.
 
-A solution would be to use a "joker", like Factor's $f$ in order to warn, when compared with an other value, that this value has not been defined yet.
-For now, the program is not able to solve this problem without removing the first lonely $1$.
+A solution could be to use a "joker", like Factor's $f$ in order to warn, when compared with an other value, that this value has not been defined yet.
+For now, the program is not able to solve this problem without removing the first isolated $1$.
 
@@
 
-It has been there since the beginning of the project, and even if{\color{blue}{many more or less 
-}} elegant solutions have been found, a lot of work {\color{blue}{remains
-}} to been done on this subject.
+This has been a problem since the beginning of the project, and even if many more or less
+elegant solutions have been found, a lot of work remains to be done on this subject.
 
@@
 
-As explained before, the use of short memory is not reliable and quite difficult to implement.
-Even though a whole implementation has been done, it has not used in final version because of its random behaviour.
+As explained above, the use of short memory is not reliable and quite difficult to implement.
+Even though a whole implementation of the use of short memory has been done, it has not linked into my final version because of its random behaviour.
 
@@
 
-This project has been an excellent way to use, at a project scale, a new and powerful language {\color{blue}{such 
-}}as Factor.
+This project has been an excellent way to use, at a project scale, a new and powerful language such as Factor.
 
-It {\color{blue}{turned out to be 
-}}difficult to use at first but incredibly efficient for this particular subject.
-The project itself proved to be harder than expected, because of its 'human' restriction.
-It has been a opportunity to consider and try to bring solutions in a little known field.
+It turned out to be difficult to use at first but incredibly efficient for this particular subject.
+The project itself proved to be harder than expected, because of its "human" restriction.
+It has been an opportunity to work and try to contribute solutions to a little known field.
 
-This was an enriching experience and {\color{blue}{well worth the time spent 
-}}working on it.
+This was an enriching experience and well worth the time spent working on it.
 
@@
 \bibitem{wikipedia_kolmogorov} Kolmogorov's Complexity on Wikiedia: \url{http://en.wikipedia.org/wiki/Kolmogorov_complexity}
+\bibitem{git} My git Hub repository: \url{https://github.com/Rekamux/Free-Project}
 

### 2011-07-03 article.tex
Corrected a little bit article

@@
 
-My warm thanks to Jon Harper, who helped me a lot through the difficult process of learning Factor, and also to my two professors,
+My warm thanks to Jon Harper, who helped me through the difficult process of learning Factor, and also to my two professors,
 Samuel Tardieu and Jean-Louis Dessalles, my supervisors, who spent time discussing my project and helping me.
@@
 
-As a student at Télécom ParisTech, I chose to follow the 'Non-classic language paradigms' course with Samuel Tardieu\cite{samuel}, 
+As a student at Télécom ParisTech, I chose to follow the 'Non-classical language paradigms' course with Samuel Tardieu\cite{samuel}, 
 while working on a free project with Jean-Louis Dessalles\cite{jld}.
@@
 optimal and human way. This will then enable us to extend that list using the compression.
-During the 'Non-classic language paradigms course, we studied uncommon languages such
+During the "Non-classical language paradigms" course, we studied uncommon languages such
 as Haskel, Scala or Factor; we also were to 
@@
 $$1\ 2\ 2\ 3\ 3\ 3$$
-Any eight-year old child would easily suggest
+Any eight-year-old child would easily suggest
 that a good continuation of this sequence would be:
@@
 
-That is why in the present version a standard \textit{binary encoding} is used to compute the complexity of a list , with 0 costing 0.
+That is why in the present version a standard \textit{binary encoding} is used to compute the complexity of a list, with 0 costing 0.
 
@@
 
-At first, I thought about using Factor's \textit{tuples}, special fields sequences which are easily sharable between descendants, as in standard \textit{Object Oriented Programming}.
+At first, I thought about using Factor's \textit{tuples}, special sequences of fields which are easily sharable between descendants, as in standard \textit{Object Oriented Programming}.
 
@@
 \begin{itemize}
-  \item{A copy operator: using its predecessor's \textit{times} field, copies a \textit{times} number of times the given argument.}
+  \item{A copy operator: using its predecessor's \textit{times} field, copies the given argument a \textit{times} number of times.}
   \item{
-    An increment operator: increments and copies a \textit{times} number of times the given argument.
+    An increment operator: increments and copies the given argument a \textit{times} number of times.
     If this argument is an operator, it will copy it by incrementing its \textit{times} field.}
@@
 Here, we can easily see that we have an increment on the digits and on the operators, but separated by one element each time.
-Using step operator, it gives:
+Using the step operator, it gives:
 $$(step\ operator\ times(4)\ gap(1)\ operator(increment\ times(1)))\ (copy\ times(1))\ 1\ 2\ 3\ 4$$
@@
 In terms of complexity, if we count 1 for each operator plus the recursive cost of all its arguments,
-the raw sequence $1\ 2\ 2\ 3\ 3\ 3\ 4\ 4\ 4\ 4$ will cost 23, while the compressed version costs 14.
+the raw sequence $1\ 2\ 2\ 3\ 3\ 3\ 4\ 4\ 4\ 4$ will cost 23, while the compressed version costs only 14.
 Hence, we can say that we have a compressed version.
@@
 
-This solution displeased Jean-Louis Dessalles, because of this not really "natural" strange step-operator, and the difficulty 
+This solution displeased Jean-Louis Dessalles, because of this not really "natural" strange step operator, and the difficulty 
 for it to be understood and used.
@@
 Therefore, I should put the argument into the operator instead of leaving it in the list.
-Then, the increment operator would have seen a sequence of copy operator incrementing at the same time their \textit{times} and \textit{argument} fields.
+Then, the increment operator would have seen a sequence of copy operators incrementing at the same time their \textit{times} and \textit{argument} fields.
 
@@
 a digit, and this is already a structural problem.
-This same field also doesn't have any meaning when applied to an increment-operator: it cannot apply to its \textit{argument} because the contained increment-operator takes care of that,
+This same field also doesn't have any meaning either when applied to an increment-operator: it cannot apply to its \textit{argument} because the contained increment-operator takes care of that,
 and hence can only apply on its \textit{times}.
@@
 $$(increment(1)(1)(arg))\ (increment(1)(2)(arg))\ (increment(1)(3)(arg))\ (increment(1)(4)(arg))$$
-
 Another time would give:
@@
 $$\{\ a_0\ a_1\ a_2\ a_3\ a_4\ a_5\ a_6\ a_7\ a_8\ a_9\ \}$$
-I use the extended indexes.
+I used the extended indexes.
 Hence, any deepness level can be reached, and there is no need to recall structural information,
@@
 Jean-Louis Dessalles wasn't really satisfied with this index solution:
-it wouldn't respect the Kantian structural form of the model
+it would not respect the Kantian structural form of the model
 (we should be able to manipulate shapes or vegetables as well, and use only them in the model).
@@
 \end{itemize}
-
 Here is an example of the use of this system on our favorite example:
@@
 
-Once an operator and a size have been chosen, we compress the sequence from the left to the right by going as far as possible and appending the result to the previous results until the rest is empty
+Once an operator and a size have been chosen,
+we compress the sequence from the left to the right by going as far as possible and appending the result to the previous results until the rest is empty
 (if the rest is not long enough to be shortened by \textit{size} elements, the program will \textcolor{red}{fail}).
@@
 
-For questions on implementation, see the program documentation as explained in my git repository README.\cite{git}
+For questions on implementation, see the program documentation as explained in my git repository README\cite{git}.
 I spent quite a long time writing it as exhaustively as possible, in order to insure a good comprehension of the program.
@@
 
-As we saw before, when we find an increment operator which is used only once (\textit{times} = 1),
+As seen before, when we find an increment operator which is used only once (\textit{times} = 1),
 its \textit{where} field doesn't mean anything, as when it is decompressed, only \textit{argument} is extracted,
@@
 The project itself proved to be harder than expected, because of its "human" restriction.
-It has been an opportunity to work and try to contribute solutions to a little known field.
+It has been an opportunity to work and try to contribute solutions to a little-known field.
 

### 2011-07-03 article.tex
Corrected a also

@@
 a digit, and this is already a structural problem.
-This same field also doesn't have any meaning either when applied to an increment-operator: it cannot apply to its \textit{argument} because the contained increment-operator takes care of that,
+This same field doesn't have any meaning either when applied to an increment-operator: it cannot apply to its \textit{argument} because the contained increment-operator takes care of that,
 and hence can only apply on its \textit{times}.
